---
title: "fig_ss_v2"
author: "Josh Alampi"
date: "7/27/2021"
output: html_document
---


#load
```{r}
#clear workspace
rm(list=ls(all=TRUE))

#load packages
library(readr); library(writexl) # for read_csv(); write_xlsx()
library(plyr) # mapvalues()
library(MASS)
library(dplyr)
library(tidyr) # for gather()
library(ggplot2)
library(ggrepel); library(ggpubr); library(scales) # extra ggplot features
library(signs) # for signs_format(), uses proper minus sign instead of hyphen
library(lmtest) # for bptest()
library(quantreg)
library(bayesQR)
select <- dplyr::select
library(rstan)
library(tidyverse)
source("functions/ggplot functions.R")
```

```{r}
data_dith <- read.csv("sim study/raw results/table_ss_JA model_2021-08-07_1000_sims.csv")
data_cnts <- read.csv("sim study/raw results/table_ss_JA moel_gold_2021-10-28_1000_sims.csv")

nrow(data_dith)
nrow(data_cnts)
```

# clean

## Count data
```{r}
data_dith <- data_dith %>% 
  filter(method != "bayes_adj_v1") # do not need adj_v1 (the default SW adjustment), as I have demonstrated earlier that it is defective. 

data_dith$method <- data_dith$method %>% # shorten the Bayesian methods' names
  mapvalues("bayes_adj_v2", "bnid") %>% 
  mapvalues("bayes", "biid") 

data_dith <- data_dith %>% # new variable: status tells us the type of data
  mutate(status = ifelse(method %in% c("bnid", "biid"),
                         "Bayesian", # Bayesian methods were not dithered
                         "Freq. (count)")) # Frequentist methods were dithered

```

## Continuous data (Bayesian methods not used)
```{r}
data_cnts <- data_cnts %>% 
  filter(is.na(method) == F) %>% # gets rid of blank method rows
  mutate(status = "Freq. (cnts)")

```

## combine
```{r}
data <- rbind(data_dith, data_cnts); nrow(data)
rm(data_dith, data_cnts)
```


# prep for analysis
## basic cleanup
```{r}
data$model <- data$model %>% # give the models proper names
  mapvalues(1, "Model 1") %>% 
  mapvalues(2, "Model 2") %>% 
  mapvalues(3, "Model 3") %>% 
  mapvalues(4, "Model 4") 

data$beta <- as.numeric(data$beta)
data$lb <- as.numeric(data$lb)
data$ub <- as.numeric(data$ub)
data$tau <- as.factor(data$tau)
```

## find interval width, remove infinite intervals
```{r}
# find interval width, with infinite intervals set to NA
data <- data %>% 
  mutate(int_width = ub - lb)

# Flag and delete infinite intervals
# Flag and delete simulations with no effect estimate
data <- data %>% 
  mutate(infin_flag = ifelse(is.infinite(lb) == T | is.infinite(ub) == T
                             # | lb > abs(10000) | ub > abs(10000)
                             ,
                             T, # interval is infinite or so large it should be removed
                             F) ) %>%
  mutate(na_flag = ifelse(is.na(beta) == T,
                          T, # no effect estimate is given due to failure to converge
                          F)) %>% 
  mutate(lb = ifelse(infin_flag == T | na_flag == T, NA, lb)) %>%
  mutate(ub = ifelse(infin_flag == T | na_flag == T, NA, ub)) %>%
  mutate(int_width = ifelse(infin_flag == T | na_flag == T, NA, int_width))

```

## find average beta and average CI width across each group of variable
```{r}
# Find the mean \hat(beta_i) across repetitions 
# Morris et al 2017 calls this value "beta-vinculum", the beta symboll with a flat line on top
data_summarised_1 <- data %>% 
  group_by(method, tau, model, n, status) %>% 
  summarise(mean_beta = mean(beta, na.rm = T)) 

# Repeat this process with mean(\hat(interval width))
data_summarised_2 <- data %>% 
  group_by(method, tau, model, n, status) %>% 
  summarise(mean_intwidth = mean(int_width, na.rm = T))


# Add this value to the dataframe
data <- merge(data, data_summarised_1, by=c("method", "tau", "model", "n", "status"))
data <- merge(data, data_summarised_2, by=c("method", "tau", "model", "n", "status"))
rm(data_summarised_1, data_summarised_2)
```

## Calculate performance measures 
```{r}
data1 <- data %>%
  mutate(n = paste0(("n = "), n)) %>% 
  
  # Performance measures
  mutate(hit_flag = ifelse(lb <= true_beta & ub >= true_beta,
                           T, #90% interval contains true_beta
                           F)) %>%
  
  mutate(hit_flag_be = ifelse(lb <= mean_beta & ub >= mean_beta,
                              T, #90% interval contains true_beta
                              F)) %>%
  
  mutate(bias = beta - true_beta) %>% 
  mutate(bias_rel = beta - mean_beta) %>%
  mutate(intwidth_rel = int_width - mean_intwidth) %>% 
  
  # Cleaning
  mutate(degen_flag = ifelse(beta == lb | beta == ub, # flag rows where beta = lb or ub
                             T, # interval is degenerate
                             F) ) %>%
  # New labels for methods
  mutate(group = ifelse(method %in% c("biid", "bnid"), 
                      "Bayesian",
                      ifelse(method %in% c("iid", "ker", "nid"), 
                             "Direct Estimation",
                             ifelse(method %in% c("riid", "rnid"),
                                    "Rank-Based",
                                    "Bootstrap"))))


# force methods to be read in a particular order
data1$method <- factor(data1$method, levels = c("iid", "nid", "ker", "riid", "rnid", 
                                            "xy", "wxy", "pwy", "mcmb", "wild", "pbs", 
                                            "biid", "bnid"))
```

Testing
```{r}
# OLD: used for testing intwidth_var
data_variability <- data %>% 
  mutate(n = paste0(("n = "), n)) %>% 
  mutate(intwidth_rel = int_width - mean_intwidth) %>% 
  filter(is.na(intwidth_rel) == F) %>% 
  mutate(infin_flag = ifelse(is.infinite(lb) == T | is.infinite(ub) == T, # flag rows w infinite intervals
                             T, # interval is degenerate
                             F) )



data_mcmb_notconverged <- data1 %>% 
  filter(method == "mcmb") %>% 
  # filter(is.na(beta) == T) %>% 
  filter(model == "Model 3")
```


## make "res" (shortens "data" into something which can actually be interpretted)
```{r}
sims <- 1000 # the number of simulations that were run. Use this for bias, empSE, and MSE
# "nsims" variable will be created to determine the number of simulations which gave non-infinite intervals. 

# Calculations for these performance measures came from Morris et al. 2017!

res <- data1 %>% 
  group_by(method, n, model, tau, group, status) %>% 
  summarise(degen = sum(degen_flag == T) / sims, # proportion of degenerate intervals
            infin = sum(infin_flag == T) / sims, # proportion of infinite intervals
            na = sum(na_flag == T) / sims, # proportion of effect estimates failing to converge
            skip = (sum(infin_flag == T | na_flag == T) / sims), # proportion of skips needed
            nsims = sims - (sims*skip), # the number of simulations with no problems
            
            # effect estimate-based performance measures
            ## Note: will only use riid, biid method for this, so I do NOT need to take infinite intervals or effect estimates that failed to converge into account (as this was only a problem for the mcmb method). Thus I use "sims" and not "nsims". 
            bias = sum(bias) / sims,
            bias_se = sqrt( sum((bias_rel)^2) / (sims * (sims -1)) ),
            
            empSE = sqrt( sum((bias_rel)^2) / (sims - 1) ),
            empSE_se = empSE / sqrt( 2  * (sims - 1) ), # empSE_se depends on empSE value
            
            MSE = sum((bias)^2) / sims,
            MSE_se = sqrt( ( sum( (bias)^2 - MSE) )^2 / sims*(sims-1) ), # MSE_se depends on MSE value
            
            
            # interval-based performance measures
            cov = sum(hit_flag == T, na.rm = T) / nsims, #### Emperical coverage probability
            cov_se = sqrt( cov * (1-cov) / nsims ), # cov_se depends on cov value
            
            cov_be = sum(hit_flag_be == T, na.rm = T) / nsims, #### Bias-adjusted Emperical Coverage Prob.
            cov_be_se = sqrt( cov_be * (1-cov_be) / nsims ), # cov_be_se depends on cov_be value
            
            intwidth_sd = sd(int_width, na.rm = T),
            
            intwidth_empSE = sqrt( sum((intwidth_rel)^2, na.rm = T) / (nsims - 1) ),
            intwidth_empSE_se = intwidth_empSE / sqrt( 2  * (nsims - 1) ), 
            
            meanbeta = mean(beta)
            ) 


res$method <- factor(res$method, levels = c("iid", "nid", "ker", "riid", "rnid", 
                                            "xy", "wxy", "pwy", "mcmb", "wild", "pbs", 
                                            "biid", "bnid"))

res <- res %>% 
  mutate(blank = F)
# res$blank <- as.factor(res$blank)



# Note: MSE, MSE_se, cov_be, cov_be_se, intwidth_sd, meanbeta are no longer used in the analysis. Left them in anyways in case I end up needing them at some point. 
```

testing
```{r}
# res_variability <- data_variability %>% 
#   group_by(method, n, model, tau, group, dithered, gold) %>% 
#   summarise(infin = sum(infin_flag == T) / sims, # frequency of infinite intervals
#            nsims = sims - (sims*infin), # the number of simulations with non-infinite intervals
#             
#            intwidth_empSE = sqrt( sum((intwidth_rel)^2, na.rm = T) / (nsims - 1) ),
#            intwidth_empSE_se = intwidth_empSE / sqrt( 2  * (nsims - 1) )
#            )

testing_res_na <- res %>% 
  filter(na != 0)

testing_res_infin <- res %>% 
  filter(infin != 0)

testing_res_degen <- res %>% 
  filter(degen != 0)

testing_res_skip <- res %>% 
  filter(skip != 0)
```


## filter "res"
```{r}
# dataset for bias and empSE
## all 11 frequentist methods give the same beta estimate.
## both Bayesian methods give the same beta estimate
res_short <- res %>% 
  filter(method %in% c("riid", "biid")) %>% 
  mutate(group_reformat = ifelse(group != "Bayesian", # Change the lables for the "group" variable
                           "Frequentist
(iid, nid, 
ker, riid, 
rnid, xy, wxy, 
pwy, mcmb, 
wild, pbs)",
                           "Bayesian
(biid, bnid)")) 


# datasets for empirical coverage prob and CI width_var

res_count <- res %>% ## Uses all 13 methods, Only count data is simulated
  filter(status != "Freq. (cnts)")

res_cnts <- res %>% ## Uses all 11 Frequentist methods (Bayesian methods ommitted), only countinuous data is simulated
  filter(status == "Freq. (cnts)")

res_count_vs_cnts <- res %>% # For comparing dith. FQR on count data vs undithered FQR on continuous data
  filter(status != "Bayesian")

```

## add superscripts
```{r}
res_count$method <- res_count$method %>% 
  mapvalues("riid", "riidᵃ") %>% 
  mapvalues("rnid", "rnidᵃ") %>% 
  mapvalues("mcmb", "mcmbᵇ") 

res_count_vs_cnts$method <- res_count_vs_cnts$method %>% 
  mapvalues("riid", "riidᵃ") %>% 
  mapvalues("rnid", "rnidᵃ") %>% 
  mapvalues("mcmb", "mcmbᵇ") 
  

```


## colours
```{r}
show_col(hue_pal()(4))
col_3 <- c("#7CAE00", "#00BFC4", "#C77CFF")
```


# Manuscript figures

## cov

### Dith, count data


#### main fig
```{r}
cov_limit <- 0.5
res_count$blank <- F
facet_margin <- 0.05

data_tmp <- res_count %>% 
  filter(n == "n = 250") %>% 
  # if coverage rate is out of bounds (below 50%), then it should be replaced with an arrow
  mutate(alpha = ifelse(cov < cov_limit, 1, 0)) %>% 
  mutate(cov_se = ifelse(cov < cov_limit, 0, cov_se)) %>%
  mutate(cov = ifelse(cov < cov_limit, 0, cov)) 
  

fig_cov_250 <- gg_geom_point(.data = data_tmp, x =tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = F,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                # title = "A) n = 250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(cov_limit,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = 0.7, yend = 0.5, 
                   x = tau, xend = tau, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(method ~ model) + 
  guides(alpha = "none") 

  
# ggsave(file = paste0("sim study/results/fig_cov_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)

# save file in format SIS wants
fig_cov_250 <- annotate_figure(fig_cov_250, 
                          top = text_grob("Joshua Alampi, Figure 2. This is the top of the figure",
                                             size = 9))


ggsave(file = paste0("sim study/results/figure 2.tiff"), width = 7.5, height = 9.5, dpi = 800)
```


#### supp
```{r}
cov_limit <- 0.5
res_count$blank <- F
facet_margin <- 0.05

data_tmp <- res_count %>% 
  filter(n == "n = 100") %>% 
  # if coverage rate is out of bounds (below 50%), then it should be replaced with an arrow
  mutate(alpha = ifelse(cov < cov_limit, 1, 0)) %>% 
  mutate(cov_se = ifelse(cov < cov_limit, 0, cov_se)) %>%
  mutate(cov = ifelse(cov < cov_limit, 0, cov)) 
  

fig_cov_100 <- gg_geom_point(.data = data_tmp, x =tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = F,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "A) n = 100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(cov_limit,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = 0.7, yend = 0.5, 
                   x = tau, xend = tau, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(method ~ model) + 
  guides(alpha = "none") 


ggsave(file = paste0("sim study/results/fig_cov_100_supp", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```


```{r}
data_tmp <- res_count %>% 
  filter(n == "n = 250") %>% 
  # if coverage rate is out of bounds (below 50%), then it should be replaced with an arrow
  mutate(alpha = ifelse(cov < cov_limit, 1, 0)) %>% 
  mutate(cov_se = ifelse(cov < cov_limit, 0, cov_se)) %>%
  mutate(cov = ifelse(cov < cov_limit, 0, cov)) 
  

fig_cov_250 <- gg_geom_point(.data = data_tmp, x =tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = F,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "B) n = 250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(cov_limit,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = 0.7, yend = 0.5, 
                   x = tau, xend = tau, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(method ~ model) + 
  guides(alpha = "none") 


ggsave(file = paste0("sim study/results/fig_cov_250_supp", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```


```{r}
data_tmp <- res_count %>% 
  filter(n == "n = 500") %>% 
  # if coverage rate is out of bounds (below 50%), then it should be replaced with an arrow
  mutate(alpha = ifelse(cov < cov_limit, 1, 0)) %>% 
  mutate(cov_se = ifelse(cov < cov_limit, 0, cov_se)) %>%
  mutate(cov = ifelse(cov < cov_limit, 0, cov)) 
  

fig_cov_500 <- gg_geom_point(.data = data_tmp, x =tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = F,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "C) n = 500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(cov_limit,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = 0.7, yend = 0.5, 
                   x = tau, xend = tau, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(method ~ model) + 
  guides(alpha = "none") 


ggsave(file = paste0("sim study/results/fig_cov_500_supp", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```


### count vs cnts
```{r}
fig_cov_cntsvscount_100 <- res_count_vs_cnts %>% 
  filter(n == "n = 100") %>% 
  filter(tau %in% c(0.1, 0.5, 0.9)) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>% 
  gg_geom_point(x = tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = T,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "A) n = 100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(0.6,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) )
  
ggsave(file = paste0("sim study/results/fig_cov_countvscnts_100", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)

fig_cov_cntsvscount_250 <- res_count_vs_cnts %>% 
  filter(n == "n = 250") %>% 
  filter(tau %in% c(0.1, 0.5, 0.9)) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>% 
  gg_geom_point(x = tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = T,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "B) n = 250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(0.6,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) )
  
ggsave(file = paste0("sim study/results/fig_cov_countvscnts_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)

fig_cov_cntsvscount_500 <- res_count_vs_cnts %>% 
  filter(n == "n = 500") %>% 
  filter(tau %in% c(0.1, 0.5, 0.9)) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>% 
  gg_geom_point(x = tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = T,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "C) n = 500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(0.6,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.1) )
  
ggsave(file = paste0("sim study/results/fig_cov_countvscnts_500", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```


```{r}
fig_cov_cntsvscount_mod4 <- res_count_vs_cnts %>% 
  filter(model == "Model 4") %>% 
  filter(tau %in% c(0.1, 0.5, 0.9)) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>% 
  gg_geom_point(x = tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal",
                facet_type = "grid", hori = "n", vert = "method",  p_dodge = T,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "Model 4", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(0.7,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.15, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) )
  
ggsave(file = paste0("sim study/results/fig_cov_countvscnts_mod4", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)

```




  mutate(intwidth_empSE = ifelse(method == "mcmb" & model == "Model 3",
         NA, intwidth_empSE) ) %>%
  mutate(intwidth_empSE_se = ifelse(method == "mcmb" & model == "Model 3",
         NA, intwidth_empSE_se) ) %>%
  mutate(blank = ifelse(method == "mcmb" & model == "Model 3",
         T, blank) ) %>% 

## intwidth var

### tau=0.9 only, dith only

#### main
```{r}
cutoff <- 10
start <- 0.5
finish <- 4


data_tmp <- res_count %>% 
  filter(tau == 0.9) %>% 
  filter(n == "n = 250") %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 0.3)) %>%
  mutate(finish = ifelse(flag ==1, finish, 0.3)) 

fig_intwidthvar_250 <- gg_geom_point(.data = data_tmp, x = method, 
                                          y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", p_dodge = F, scales = "free_y",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                # title = "A) n = 100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 


# ggsave(file = paste0("sim study/results/fig_intwidthvar_250_main", "_",  Sys.Date(), ".png"), width = 7.5, height = 3.5, dpi = 300)

fig_intwidthvar_250 <- annotate_figure(fig_intwidthvar_250, 
                          top = text_grob("Joshua Alampi, Figure 3. This is the top of the figure",
                                             size = 9))

ggsave(file = paste0("sim study/results/figure 3.tiff"), width = 7.5, height = 3.5, dpi = 800)
```

#### supp


```{r}
cutoff <- 10
start <- 1
finish <- 7

data_tmp <- res_count %>% 
  filter(tau == 0.9) %>% 
  filter(n == "n = 100") %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 0.3)) %>%
  mutate(finish = ifelse(flag ==1, finish, 0.3)) 

fig_intwidthvar_100 <- gg_geom_point(.data = data_tmp, x = method, 
                                          y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", p_dodge = F, scales = "free_y",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                title = "A) n = 100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 


cutoff <- 10
start <- 0.5
finish <- 4

data_tmp <- res_count %>% 
  filter(tau == 0.9) %>% 
  filter(n == "n = 250") %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 0.3)) %>%
  mutate(finish = ifelse(flag ==1, finish, 0.3)) 

fig_intwidthvar_250 <- gg_geom_point(.data = data_tmp, x = method, 
                                          y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", p_dodge = F, scales = "free_y",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                title = "B) n = 250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 


cutoff <- 5
start <- 0.25
finish <- 0.9

data_tmp <- res_count %>% 
  filter(tau == 0.9) %>% 
  filter(n == "n = 500") %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 0.3)) %>%
  mutate(finish = ifelse(flag ==1, finish, 0.3)) 

fig_intwidthvar_500 <- gg_geom_point(.data = data_tmp, x = method, 
                                          y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", p_dodge = F, scales = "free_y",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                title = "C) n = 500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 



fig_intwidthvar_all <- ggarrange(fig_intwidthvar_100, fig_intwidthvar_250, fig_intwidthvar_500,
                                 common.legend = T, ncol = 1, legend = "bottom")

ggsave(file = paste0("sim study/results/fig_intwidthvar_all", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```


### Fig: GS vs dith
```{r}
legend.margin_inch <- 0.0000000000000000000000625
legend.spacing <- 0.00000000000000000000000000625

cutoff <- 20
start <- 1
finish <- 15


data_tmp <- res_count_vs_cnts %>% 
  filter(n == "n = 100") %>% 
  filter(tau == 0.9) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 1.4)) %>%
  mutate(finish = ifelse(flag ==1, finish, 1.4)) 

fig_intwidthvar_g_vs_c_100 <- gg_geom_point(.data = data_tmp,
  x = method, y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal", 
                legend.margin_inch = legend.margin_inch, legend.spacing = legend.spacing,
                facet_type = "grid", hori = "model",  
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                title = "A) n = 100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 


cutoff <- 5
start <- 0.5
finish <- 4


data_tmp <- res_count_vs_cnts %>% 
  filter(n == "n = 250") %>% 
  filter(tau == 0.9) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 0.6)) %>%
  mutate(finish = ifelse(flag ==1, finish, 0.6)) 

fig_intwidthvar_g_vs_c_250 <- gg_geom_point(.data = data_tmp,
  x = method, y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal", 
                legend.margin_inch = legend.margin_inch, legend.spacing = legend.spacing,
                facet_type = "grid", hori = "model",  
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                title = "B) n = 250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 




cutoff <- 5
start <- 0.2
finish <- 0.8


data_tmp <- res_count_vs_cnts %>% 
  filter(n == "n = 500") %>% 
  filter(tau == 0.9) %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  mutate(flag = ifelse(intwidth_empSE > cutoff, 1, 0)) %>% 
  mutate(intwidth_empSE = ifelse(flag ==1, NA, intwidth_empSE)) %>%   
  mutate(intwidth_empSE_se = ifelse(flag ==1, NA, intwidth_empSE_se)) %>%
  mutate(alpha = ifelse(flag ==1, 1, 0)) %>% 
  mutate(method = fct_rev(method)) %>% 
  mutate(start = ifelse(flag ==1, start, 0.4)) %>%
  mutate(finish = ifelse(flag ==1, finish, 0.4)) 

fig_intwidthvar_g_vs_c_500 <- gg_geom_point(.data = data_tmp,
  x = method, y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal", 
                legend.margin_inch = legend.margin_inch, legend.spacing = legend.spacing,
                facet_type = "grid", hori = "model",  
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile regression method",
                title = "C) n = 500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) ) +
  geom_segment(data = data_tmp, 
               aes(y = start, yend = finish,
                   x = method, xend = method, alpha = alpha),
               arrow = arrow(length = unit(0.05, "inch"))) +
  scale_alpha(range = c(0,1)) + 
  facet_grid(. ~ model, scales = "free") + 
  guides(alpha = "none") 



fig_intwidthvar_g_vs_c_all <- ggarrange(fig_intwidthvar_g_vs_c_100, fig_intwidthvar_g_vs_c_250,
                                        fig_intwidthvar_g_vs_c_500,
                                        common.legend = T, ncol = 1, legend = "bottom")

ggsave(file = paste0("sim study/results/fig_intwidthvar_g_vs_c_all", "_",  Sys.Date(), ".png"), width = 7.5, height = 10.5, dpi = 300)

```

### Not used: all tau, dith only
```{r}
fig_intwidthvar_100 <- res_count %>% 
  filter(n == "n = 100") %>% 
  mutate(intwidth_empSE = ifelse(method == "mcmb" & tau != 0.3 & model == "Model 3",
         NA, intwidth_empSE) ) %>% 
  mutate(intwidth_empSE_se = ifelse(method == "mcmb" & tau != 0.3 & model == "Model 3",
         NA, intwidth_empSE_se) ) %>% 
  mutate(blank = ifelse(method == "mcmb" & tau != 0.3 & model == "Model 3",
         T, blank) ) %>% 
  gg_geom_point(x = tau, y = intwidth_empSE, 
                ymin = intwidth_empSE - intwidth_empSE_se, ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1, 4), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                text_size_minor = 7, text_size_major = 9, 
                yint = NULL, coord_flip = T, ystrip_angle = 0) 


ggsave(file = paste0("sim study/results/fig_intwidthvar_100", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```

```{r}
fig_intwidthvar_250 <- res_count %>% 
  filter(n == "n = 250") %>% 
  mutate(intwidth_empSE = ifelse(method == "mcmb" & tau %in% c(0.3,0.9) & model == "Model 3",
         NA, intwidth_empSE) ) %>%
  mutate(intwidth_empSE_se = ifelse(method == "mcmb" & tau %in% c(0.3,0.9) & model == "Model 3",
         NA, intwidth_empSE_se) ) %>%
  mutate(blank = ifelse(method == "mcmb" & tau %in% c(0.3,0.9) & model == "Model 3",
         F, blank) ) %>% 
  gg_geom_point(x = tau, y = intwidth_empSE, 
                ymin = intwidth_empSE - intwidth_empSE_se, ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1, 4), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                text_size_minor = 7, text_size_major = 9, 
                yint = NULL, coord_flip = T, ystrip_angle = 0) 


ggsave(file = paste0("sim study/results/fig_intwidthvar_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```

```{r}
fig_intwidthvar_500 <- res_count %>% 
  filter(n == "n = 500") %>% 
  mutate(intwidth_empSE = ifelse(method == "mcmb" & tau %in% c(0.5,0.9) & model == "Model 3",
         NA, intwidth_empSE) ) %>%
  mutate(intwidth_empSE_se = ifelse(method == "mcmb" & tau %in% c(0.5,0.9) & model == "Model 3",
         NA, intwidth_empSE_se) ) %>%
  mutate(blank = ifelse(method == "mcmb" & tau %in% c(0.5,0.9) & model == "Model 3",
         T, blank) ) %>% 
  gg_geom_point(x = tau, y = intwidth_empSE, 
                ymin = intwidth_empSE - intwidth_empSE_se, ymax = intwidth_empSE + intwidth_empSE_se,
                shape = blank, shape_vec = c(1, 4), shape_title = NULL,
                colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                text_size_minor = 7, text_size_major = 9, 
                yint = NULL, coord_flip = T, ystrip_angle = 0) 


ggsave(file = paste0("sim study/results/fig_intwidthvar_500", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```


## Special fig: count vs cnts 
```{r}
legend.margin_inch <- 0.0000000000000000000000625
legend.spacing <- 0.00000000000000000000000000625

# Bias
fig__sp_bias <- res_short %>% 
  filter(status != "Bayesian") %>%
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "A) Bias", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

# Variability of effect estimates
fig_sp_empSE <- res_short %>% 
  filter(status != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard error of point estimates \n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "B) Variability of point estimates",
                text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )


fig_sp_cov <- res_count_vs_cnts %>% 
  filter(n == "n = 250") %>% 
  filter(method == "xy") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>% 
  gg_geom_point(x = tau, y = cov, ymin = cov - cov_se, ymax = cov + cov_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", 
                colour_vec = col_3,
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "method",  p_dodge = T,
                ylab = "Empirical covarage probabilities \n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "C) Empirical coverage probabilities", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9, yint = 0.9, 
                limits = c(0.8,1), coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.05) )

fig_sp_intwidthvar <- res_count_vs_cnts %>% 
  filter(n == "n = 250") %>% 
  # filter(tau == 0.9) %>% 
  filter(method == "xy") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>% 
  gg_geom_point(x = tau, y = intwidth_empSE, ymin = intwidth_empSE - intwidth_empSE_se, 
                ymax = intwidth_empSE + intwidth_empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                colour = group, col_title = "Quantile regression method family", colour_vec = col_3,
                legend.direction = "horizontal", 
                legend.margin_inch = legend.margin_inch, legend.spacing = legend.spacing,
                facet_type = "grid", hori = "model",  vert = "method",
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard deviation of 90% intervals \n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "D) Variability of interval widths",
                text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.05) )

fig_sp_countvscnts <- ggarrange(fig__sp_bias, fig_sp_empSE, 
                     fig_sp_cov, fig_sp_intwidthvar,
                     common.legend = T, ncol = 1, legend = "bottom")

# ggsave(file = paste0("sim study/results/fig_sp_countvscnts", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)

fig_sp_countvscnts <- annotate_figure(fig_sp_countvscnts, 
                          top = text_grob("Joshua Alampi, Figure 4. This is the top of the figure",
                                             size = 9))

ggsave(file = paste0("sim study/results/figure 4.tiff"), width = 7.5, height = 9.5, dpi = 800)
```




## bias
### dith FQR vs undith BQR
```{r}
# n = 250

fig_bias_count_250 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                # title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.3, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

ggsave(file = paste0("sim study/results/fig_bias_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 3, dpi = 300)
```

```{r}
# all n

fig_bias_count_100 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 100") %>% 
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "A) n=100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.3, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

fig_bias_count_250 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.3, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

fig_bias_count_500 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 500") %>% 
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "C) n=500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.3, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

fig_bias_all <- ggarrange(fig_bias_count_100, fig_bias_count_250, fig_bias_count_500,
                          common.legend = T, ncol = 1, legend = "bottom")

ggsave(file = paste0("sim study/results/fig_bias", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```

### count vs cnts
```{r}
# n = 250

fig_bias_countvscnts_250 <- res_short %>% 
  filter(status != "Bayesian") %>%
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                # title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )


ggsave(file = paste0("sim study/results/fig_bias_countvscnts_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 3, dpi = 300)
```


```{r}
# all n

fig_bias_cvsc_100 <- res_short %>% 
  filter(n == "n = 100") %>% 
  filter(group != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "A) n=100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.005) )


fig_bias_cvsc_250 <- res_short %>% 
  filter(n == "n = 250") %>% 
  filter(group != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

fig_bias_cvsc_500 <- res_short %>% 
  filter(n == "n = 500") %>% 
  filter(group != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  gg_geom_point(x = tau, y = bias, ymin = bias-bias_se, ymax = bias + bias_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Bias (+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                title = "C) n=500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) +
  scale_y_continuous(labels = number_format(accuracy = 0.005) )

fig_bias_all <- ggarrange(fig_bias_cvsc_100, fig_bias_cvsc_250, fig_bias_cvsc_500,
                          common.legend = T, ncol = 1, legend = "bottom")

ggsave(file = paste0("sim study/results/fig_bias_countvscnts", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```

## empSE
### dith FQR vs undith BQR
```{r}
# n = 250

fig_empSE_count_250 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                # title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

ggsave(file = paste0("sim study/results/fig_empSE_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 3, dpi = 300)
```

```{r}
# all n

fig_empSE_count_100 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 100") %>% 
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "A) n=100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) )

fig_empSE_count_250 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )

fig_empSE_count_500 <- res_short %>% 
  filter(status != "Freq. (cnts)") %>% 
  filter(n == "n = 500") %>% 
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = blank, shape_vec = c(1), shape_title = NULL,
                # colour = group, col_title = "Quantile regression method family", legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = F, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "C) n=500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) 

fig_empSE_all <- ggarrange(fig_empSE_count_100, fig_empSE_count_250, fig_empSE_count_500,
                          common.legend = T, ncol = 1, legend = "bottom")

ggsave(file = paste0("sim study/results/fig_empSE", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```

### count vs cnts
```{r}
# n = 250

fig_empSE_countvscnts_250 <- res_short %>% 
  filter(status != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                           "Count data, dithered",
                           "Continuous data, not dithered")) %>%
  filter(n == "n = 250") %>% 
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)", 
                xlab = "Quantile",
                # title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.1, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )


ggsave(file = paste0("sim study/results/fig_empSE_countvscnts_250", "_",  Sys.Date(), ".png"), width = 7.5, height = 3, dpi = 300)
```


```{r}
fig_empSE_cvsc_100 <- res_short %>% 
  filter(n == "n = 100") %>% 
  filter(group != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                                  "Count data, dithered",
                                  "Continuous data, not dithered")) %>%
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression approach",
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "A) n=100", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.1) )


fig_empSE_cvsc_250 <- res_short %>% 
  filter(n == "n = 250") %>% 
  filter(group != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                                  "Count data, dithered",
                                  "Continuous data, not dithered")) %>%
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "B) n=250", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05) + 
  scale_y_continuous(labels = number_format(accuracy = 0.01) )


fig_empSE_cvsc_500 <- res_short %>% 
  filter(n == "n = 500") %>% 
  filter(group != "Bayesian") %>% 
  mutate(status_reformat = ifelse(status == "Freq. (count)",
                                  "Count data, dithered",
                                  "Continuous data, not dithered")) %>%
  gg_geom_point(x = tau, y = empSE, ymin = empSE-empSE_se, ymax = empSE + empSE_se,
                shape = status_reformat, shape_vec = c(0, 1), shape_title = "Status",
                # colour = group, col_title = "Quantile regression method family", 
                legend.direction = "horizontal",
                facet_type = "grid", hori = "model", vert = "group_reformat", 
                p_dodge = T, scales = "free_x",
                ylab = "Empirical standard error of point estimates\n(+/- 1 Monte Carlo standard error)",
                xlab = "Quantile",
                title = "C) n=500", text_size_title = 10,
                text_size_minor = 7, text_size_major = 9,
                yint = NULL, coord_flip = T, ystrip_angle = 0,
                panel.spacing.x = 0.2, panel.spacing.y = 0.05)

fig_empSE_all <- ggarrange(fig_empSE_cvsc_100, fig_empSE_cvsc_250, fig_empSE_cvsc_500,
                          common.legend = T, ncol = 1, legend = "bottom")

ggsave(file = paste0("sim study/results/fig_empSE_countvscnts", "_",  Sys.Date(), ".png"), width = 7.5, height = 9.5, dpi = 300)
```





